Synthetic algebraic geometry and the phenomenon of nongeometric sequents

### 2018-04-05 slides-pssl103.tex
Small layout changes

\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{tabto}
\usepackage{xstring}
\usepackage{soul}\setul{0.3ex}{}
\usepackage[all]{xy}
\xyoption{rotate}
\usepackage{tikz}
\usetikzlibrary{calc,shapes.callouts,shapes.arrows,patterns}
\hypersetup{colorlinks=true}
\usepackage{multimedia}
\newcommand{\video}[2]{\movie[width=#2,height=#2,autostart,loop,poster]{}{#1}}

@@

\setbeamertemplate{footline}{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=2.25ex,dp=1ex,right,rightskip=1mm,leftskip=1mm]{}%
    \inserttitle \hfill
    \insertframenumber\,/\,\inserttotalframenumber
  \end{beamercolorbox}%
  \vskip0pt%
}

@@

\begin{frame}[c]
  \centering
  \includegraphics[scale=0.3]{images/external-internal-small}
  \medskip

@@

  103rd Peripatetic Seminar on Sheaves and Logic (Brno) \\
  April 7th, 2018
  \par
\end{frame}

@@

\newcommand{\intex}[3]{#1 \quad #2\par #3\medskip}

\begin{frame}{Curious universes}
  \small
  \intex{
    $\Eff \models \text{``There are infinitely many prime numbers.''}$
  }{\textcolor{green!90}{\cmark}}{
    External meaning: There is a Turing \hil{machine} producing arbitrarily many prime
    numbers.
  }

  \intex{
    $\Eff \not\models \text{``Any Turing machine halts or doesn't halt.''}$
  }{\textcolor{red!80}{\xmark}}{
    External meaning: There is a \hil{halting oracle} which determines whether
    any given machine halts or doesn't halt.
  }

  \intex{
    $\Sh(X) \not\models \text{``Any cont. function with opposite signs has
    a zero.''}$
  }{\textcolor{red!80}{\xmark}}{
    External meaning: Zeros can be picked \hil{locally continuously} in
    continuous families of continuous functions.
  }

  \vspace*{-1em}
  \hfill\video{zeros-in-families.mp4}{2cm}
\end{frame}

@@

  \vspace*{-2em}
  \begin{varblock}{11cm}{}  %Fundamental theorem about classifying toposes}
    For a \hil{geometric sequent}~$\varphi \seq \psi$, the following
    are equivalent:
    \begin{enumerate}
      \item The theory~$\TT$ \hil{proves}~$\varphi \seq \psi$. \\[-1em]
      \item $\forall \vec x\_ (\varphi \Rightarrow \psi)$ holds
      \hil{for all models} of~$\TT$ in all toposes. \\[-1em]
      \item $\forall \vec x\_ (\varphi \Rightarrow \psi)$ holds
      for the \hil{generic model} of~$\TT$ in its \hil{classifying topos}.
    \end{enumerate}
  \end{varblock}

>>>>

\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{multicol}
\usepackage{tabto}
\usepackage{xstring}
\usepackage{soul}\setul{0.3ex}{}
\usepackage[all]{xy}
\xyoption{rotate}
\usepackage{tikz}
\usetikzlibrary{calc,shapes.callouts,shapes.arrows,patterns}
\hypersetup{colorlinks=true}
\usepackage{multimedia}
\newcommand{\video}[2]{\movie[width=#2,height=#2,autostart,loop,poster]{}{#1}}
\hypersetup{colorlinks=false}

@@

\setbeamertemplate{footline}{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=2.25ex,dp=1ex,right,rightskip=1mm,leftskip=1mm]{}%
    \hfill
    \insertframenumber\,/\,\inserttotalframenumber
  \end{beamercolorbox}%
  \vskip0pt%
}

@@

\begin{frame}[c]
  \centering
  \medskip
  \includegraphics[scale=0.3]{images/external-internal-small}
  \medskip

@@

  103rd Peripatetic Seminar on Sheaves and Logic in Brno \\
  April 7th, 2018
  \par
\end{frame}

@@

\newcommand{\intex}[3]{#1 \quad #2\par #3\bigskip\medskip}

\begin{frame}{Curious universes}
  \begin{changemargin}{-1.1em}{0em}
    \small
    \begin{itemize}
      \item \intex{
        $\Eff \models \text{``There are infinitely many prime numbers.''}$
      }{\textcolor{green!90}{\cmark}}{
        External meaning: There is a Turing \hil{machine} producing arbitrarily many prime
        numbers.
      }

      \item \intex{
        $\Eff \not\models \text{``Any Turing machine halts or doesn't halt.''}$
      }{\textcolor{red!80}{\xmark}}{
        External meaning: There is a \hil{halting oracle} which determines whether
        any given machine halts or doesn't halt.
      }

      \item \intex{
        $\Sh(X) \not\models \text{``Any cont. function with opposite signs has
        a zero.''}$
      }{\textcolor{red!80}{\xmark}}{
        External meaning: Zeros can be picked \hil{locally continuously} in
        continuous families of continuous functions.
      }
    \end{itemize}
  \end{changemargin}

  \vspace*{-2em}
  \hfill\video{zeros-in-families.mp4}{2cm}
\end{frame}

@@

  \vspace*{-2em}
  \begin{varblock}{11cm}{}  %Fundamental theorem about classifying toposes}
    For a \hil{geometric sequent}~$\forall \vec x\_ (\varphi \Rightarrow \psi)$, the following
    are equivalent:
    \begin{enumerate}
      \item It is \hil{provable} by~$\TT$. \\[-1em]
      \item It holds
      \hil{for all models} of~$\TT$ in all toposes. \\[-1em]
      \item It holds
      for the \hil{generic model} of~$\TT$ in its \hil{classifying topos}.
    \end{enumerate}
  \end{varblock}
